Revisiting Multi-Domain Machine Translation

### 2020-08-20 2020/tacl2020/rebuttal.tex

\\
\begin{itemize}
\item[*] You provide some useful experimental results on various MDMT approaches. To benefit from your results, we need access to the same segmentation of train/dev/test sets that I hope you will provide to the community.
\textcolor{blue}{Supplementary details regarding the settings used in our experiments have been added in a new Appendix YYY.\fyTodo{Fix the appendix.}. We will also distribute the detailed composition of our train / dev / test split upon acceptance of the paper.}

@@

\\
\item[*] Please define Lambda coefficients in lines 142 and 146.
\\
\textcolor{blue}{We formalize the data distribution as a mixture of several in-domain distribution. $\lambda$ correspond to the mixing weights, that also define the prior distribution on domains. We hypothesize that training distribution is different from testing distribution, so we have need notation for two different mixtures. This has been clarified in the text (see line~XXX) \fyTodo{add lines}}

@@

\\
\item[*] L. 681-683: I don’t see it as a failure, and I think it is a property (requirement) as you describe in the definition of [P4-ERR], we expect deterioration in the presence of tag error. Am I right?
\\
\textcolor{blue}{This is correct - a drop is performance is expected when using wrong domain tags; [P4-ERR] is however about robustness against domain errors and a good MDMT system should keep this loss small. This is not what we see for the systems that use domain tags in testing.}

@@

\\
\item To some extent, I dislike Table~5. When not reading carefully, the difference values could be interpreted as differences wrt. scores in Table 3. (Except that the numbers would be wrong...) Differences wrt. to Table 3 are important and it took me a while to obtain an overview for myself. Furthermore, it should be immediately obvious which number is "resumed training" and which is training from scratch. (It isn't from the table caption alone.)
\\
\textcolor{red}{In Table 5, we report the difference in performance between 2 situations: resuming training and training from beginning with 7 domains. We would like to report the difference wrt to Table 3 in the later version of the paper. We agree that the comparison to Table 3 is also important, because helps assess the impact of a new domain to the previously learned domains.}fytodo{What should we do about it ?}

@@

\\
\item For \system{DC-Feat}, is the feature added for each word or for each subword token? Is it attached to the word (increasing the vocabulary size a lot) or does it remain a separate token (increasing the input length a lot)?
\\
\textcolor{blue}{\system{DC-Feat} uses a small fixed embedding representing the domain. It is concatenated to every word embedding. The use of \system{DC-Feat} increases the size of the input embedding, but does not increase the vocabulary size nor the input length. This is clarified in the Appendix containing supplementary implementation details.}

@@

\\
\item How is the domain-weighted average (WAVG) calculated? Is the weight determined by proportion of the respective domain in the training data?
\\
\textcolor{blue}{This is correct: the domain-weighted average is computed by weighting the performance of the model in each domain test with the proportion of the respective domain in the training data.}

@@

\\
\item Wasn't it possible to use standard test sets? The "REL" Bleu scores are suspiciously high and there might be considerable redundancy in the data, or rather: training data contaminated with test data. (Since duplicates are possible, have you verified that the test sentences don't still appear in the remaining training data?)
\\
\textcolor{blue}{There are standard test sets for some domains such as medical, IT, news and talk, but we could not find any standard test sets for the other domains including religion, law and bank. We carefully removed every duplicate sentence in all the corpora. In our opinion, the reason why the models achieve extremely high scores in the \domain{rel} domain is because texts in this domain is very repetitive and often predictable.}\fyTodo{sentence length ?, diversity index of vocab ?}

@@

\end{itemize}

Other (minor) remarks:

\begin{itemize}
\item From the UFAL medical corpus, please say that you're using the indomain sections only (which is mostly PatTR Medical).
\\
\textcolor{blue}{From the UFAL medical corpus of the language pair En-Fr, we select only sentences in categories including EMEA, ParTR, CESTA, ECDC. This is now mentioned in the text (lines XXX)}\fyTodo{Add lines num}
\\
\item The \system{DC-Feat} and \system{DC-Tag} lines in Table 5 should be swapped in order to be in line with Tables 3 and 4.
  \\
  \textcolor{blue}{We have changed the order of "DC-Feat" and "DC-Tag" to be consistent with tables 3 and 4.}
\end{itemize}

The remaining style issues have also been corrected.

### 2020-08-20 2020/tacl2020/multidomain.tex
more fixes and rebuttal - new reference

\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}
\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}

@@

A third series of motivations are of statistical nature. The training data available for each domain is usually unevenly distributed, and domain-specific systems trained or adapted on small datasets are likely to have a high variance and generalize poorly. For some test domains, there may even be no data at all \cite{Farajian17neural}. Training mix-domain systems is likely to reduce this variance, at the expense of a larger statistical bias \cite{Clark12onesystem}. Under this view, MDMT would be especially beneficial for domains with little training data. This is observed for multilingual MT from English: an increase for under-resourced languages due to positive transfer, at the cost of a decrease in performance for well-resourced languages \cite{Arivazhagan19massively}.

@@

\begin{table*}
  \begin{tabular}{|p{2.5cm}|*{9}{r|}} \hline \footnotesize
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline
     \system{Mixed-Nat}  & 37.1  & 54.1  & 49.6	& 34.1  & 42.1	& 77.0 & 28.9 & 40.8	& 49.0 \\ 
%    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & 23.5 & 41.1 & 49.4 \\
%    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & **** & 42.8 & 53.8 \\
    \hline%\hline
    \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5  & 41.4 & 49.9\\[-2pt]
%                                   & 38.0  & 54.4   & 49.2    & \SW{33.6}  &  \SW{42.7}  &\SW{75.3}  & \SW{28.1}  & & 48.9\\
                   & \scriptsize +0.3  & \scriptsize -0.1   & \scriptsize -0.6    & \scriptsize \SW{-1.1}  &  \scriptsize \SW{-1.3}  & \scriptsize \SW{-3.5}  & \scriptsize \SW{-1.4}  & \scriptsize -0.1 & \scriptsize \SW{-1.2}\\

@@

\subsection{Automatic domains \label{ssec:autodomains}}
In this section, we experiment with automatic domains, obtained by clustering sentences into $k=30$ classes using the k-means algorithm based on generic sentence representations obtained via mean pooling as in Section~\ref{ssec:corpora}. This allows us to evaluate requirement [P7-scale], training and testing our systems as if these domains were genuine. We also note that many of these classes are mere split of the large \domain{med}, while a fewer number of classes are mix of two existing domains. We are thus in a position to reiterate at a larger scale the measurements of Section~\ref{ssec:redomains} and test whether multi-domain systems can effectively take advantage from the cross-domain similarities, and to eventually perform better than fine-tuning.

@@

\begin{table*}[t]
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
  %    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
  %     \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
  %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.5 & \SW{54.0} & 49.0   & 33.6 & \SW{42.2} & \SW{76.7} & 41.6 & 49.0 \\%    & 21.8 \\
    \system{DC-Feat}      & 37.3  & 54.2 & 49.3   & 33.6 & \SW{41.9} & \SW{75.8} & 40.8 & \SW{48.7}  \\% & \SW{21.7} \\
    \system{LDR}     & 37.4   & 54.1 & \SW{48.7} & \SW{32.5} & \SW{41.4} & \SW{75.9} & 39.1 & \SW{48.3}         \\% & 22.1 \\ 
    \system{TTM}            & 37.4 & \SW{53.7} & 48.9 & 32.8 & 41.3 & \SW{75.8} & 40.7 & \SW{48.3}   \\% &  23.4 \\
    \system{DM}             & 35.4 & 49.3  & 45.2 & 29.7 & 37.1 & \SW{60.0} & 37.8 & 42.8 \\ % & 22.6\\
    \system{ADM}           & 36.1 & 53.5  & 48.0 & 32.0 & 41.1 & 72.1 & 39.5 & 47.1\\% & 23.3 \\
    \system{WDCMT}       & 35.6 & 53.1 & 48.4 & 30.5 & \SW{37.7} & \SW{56.0} & 38.5 & 43.6 \\ % & 20.4 \\ 
    \system{MDL Res}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 41.2 & \SB{50.7}\\%  & \SW{21.2} \\
     \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets. Significancy tests are for comparisons with the 6-domain scenario.}
  \label{tab:subdomains}
  \fyDone{Fill the table with correct results,}\fyDone{Change wavg and avg}
\end{table*}

@@

%; scores are reported separately per domain, suggesting that all domains are equally important at test time.
% Adversarial adpatation is used in many domains
% for QA @misc{lee2019domainagnostic,
%    title={Domain-agnostic Question-Answering with Adversarial Training},
%    author={Seanie Lee and Donggyu Kim and Jangwon Park},
%    year={2019},
%    eprint={1910.09342},
%    archivePrefix={arXiv},
%    primaryClass={cs.CL}
%}, NLU and many others

Multi-domain translation was already proposed for statistical MT, either considering as we do multiple sources of training data (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}), or domains made of multiple topics\fyDone{you mean multiple topics?} \cite{Eidelman12topic,Hasler14dynamic-topic}.\fyDone{Add also topic models refs} Two main strategies were considered: instance-based, involving a measure of similarities between train and test domains; feature-based, where domain/topic labels give rise to additional features.

@@

Techniques proposed by \cite{Britz17mixing} aim to ensure that domain information is actually used in a mix-domain system. Three methods are considered, using either domain classification (or domain normalization, via adversarial training) on the source or target side. There is no clear winner in either of the three language pairs considered. One contribution of this work is the idea of normalizing representations through adversarial training, so as to make the mixture of heterogeneous data more effective; representation normalization has since proven a key ingredient in multilingual transfer learning.
The same basic techniques (parameter sharing, automatic domain identification / normalization) are simultaneously at play in \cite{Zeng18multidomain,Su19exploring}: in this approach, the lower layers of the MT use auxiliary classification tasks to disentangle domain specific representations on the one hand from domain-agnostic representation on the other hand. These representations are then processed as two separate inputs, then recombined to compute the translation.

>>>>

\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{{#1}}}
\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}

@@

A third series of motivations are of statistical nature. The training data available for each domain is usually unevenly distributed, and domain-specific systems trained or adapted on small datasets are likely to have a high variance and generalize poorly. For some test domains, there may even be no data at all \cite{Farajian17neural}. Training mix-domain systems is likely to reduce this variance, at the expense of a larger statistical bias \cite{Clark12onesystem}. Under this view, MDMT would be especially beneficial for domains with little training data \revision{(see~\cite{Sharaf20metalearning} for a discussion of DA in low resource conditions and a meta-learning based approach to this problem)}. This is observed for multilingual MT from English: an increase for under-resourced languages due to positive transfer, at the cost of a decrease in performance for well-resourced languages \cite{Arivazhagan19massively}.

@@

\begin{table*}
  \centering
  \begin{tabular}{|p{2.5cm}|*{9}{r|}} \hline \footnotesize
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline
     \system{Mixed-Nat}  & 37.1  & 54.1  & 49.6	& 34.1  & 42.1	& 77.0 & 28.9 & 40.8	& 49.0 \\ 
%    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & 23.5 & 41.1 & 49.4 \\
%    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & **** & 42.8 & 53.8 \\
    \hline%\hline
    \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5  & 41.4 & 49.9\\[-2pt]
%                                   & 38.0  & 54.4   & 49.2    & \SW{33.6}  &  \SW{42.7}  &\SW{75.3}  & \SW{28.1}  & & 48.9\\
                   & \scriptsize +0.3  & \scriptsize -0.1   & \scriptsize -0.6    & \scriptsize \SW{-1.1}  &  \scriptsize \SW{-1.3}  & \scriptsize \SW{-3.5}  & \scriptsize \SW{-1.4}  & \scriptsize -0.1 & \scriptsize \SW{-1.2}\\

@@

\subsection{Automatic domains \label{ssec:autodomains}}
In this section, we experiment with automatic domains, obtained by clustering sentences into $k=30$ classes using the k-means algorithm based on generic sentence representations obtained via mean pooling as in Section~\ref{ssec:corpora}. This allows us to evaluate requirement [P7-scale], training and testing our systems as if these domains were genuine. We also note that many of these classes are mere split of the large \domain{med}, while a fewer number of classes are mixtures of two existing domains. We are thus in a position to reiterate at a larger scale the measurements of Section~\ref{ssec:redomains} and test whether multi-domain systems can effectively take advantage from the cross-domain similarities, and to eventually perform better than fine-tuning.

@@

\begin{table*}[t]
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
  %    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
  %     \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
  %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.5 & \SW{54.0} & 49.0   & 33.6 & \SW{42.2} & \SW{76.7} & 41.6 & 49.0 \\%    & 21.8 \\
    \system{DC-Feat}      & 37.3  & 54.2 & 49.3   & 33.6 & \SW{41.9} & \SW{75.8} & 40.8 & \SW{48.7}  \\% & \SW{21.7} \\
    \system{LDR}             & 37.4   & 54.1 & \SW{48.7} & \SW{32.5} & \SW{41.4} & \SW{75.9} & 39.1 & \SW{48.3}         \\% & 22.1 \\ 
    \system{TTM}            & 37.4 & \SW{53.7} & 48.9 & 32.8 & 41.3 & \SW{75.8} & 40.7 & \SW{48.3}   \\% &  23.4 \\
    \system{DM}             & 35.4 & 49.3  & 45.2 & 29.7 & 37.1 & \SW{60.0} & 37.8 & 42.8 \\ % & 22.6\\
    \system{ADM}           & 36.1 & 53.5  & 48.0 & 32.0 & 41.1 & 72.1 & 39.5 & 47.1\\% & 23.3 \\
    \system{WDCMT}       & 35.6 & 53.1 & 48.4 & 30.5 & \SW{37.7} & \SW{56.0} & 38.5 & 43.6 \\ % & 20.4 \\ 
    \revision{\system{FT-Block}}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 41.2 & \SB{50.7}\\%  & \SW{21.2} \\
    \system{MDL Res}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 41.2 & \SB{50.7}\\%  & \SW{21.2} \\
     \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets. Significancy tests are for comparisons with the 6-domain scenario.}
  \label{tab:subdomains}
  \fyDone{Fill the table with correct results,}\fyDone{Change wavg and avg}
\end{table*}

@@

%; scores are reported separately per domain, suggesting that all domains are equally important at test time.
% Adversarial adpatation is used in many domains
% for QA @misc{lee2019domainagnostic,
%    title={Domain-agnostic Question-Answering with Adversarial Training},
%    author={Seanie Lee and Donggyu Kim and Jangwon Park},
%    year={2019},
%    eprint={1910.09342},
%    archivePrefix={arXiv},
%    primaryClass={cs.CL}
%}, NLU and many others
Multi-domain translation was already proposed for statistical MT, either considering as we do multiple sources of training data (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}), or domains made of multiple topics\fyDone{you mean multiple topics?} \cite{Eidelman12topic,Hasler14dynamic-topic}.\fyDone{Add also topic models refs} Two main strategies were considered: instance-based, involving a measure of similarities between train and test domains; feature-based, where domain/topic labels give rise to additional features.

@@

Techniques proposed by \cite{Britz17mixing} aim to ensure that domain information is actually used in a mix-domain system. Three methods are considered, using either domain classification (or domain normalization, via adversarial training) on the source or target side. There is no clear winner in either of the three language pairs considered. One contribution of this work is the idea of normalizing representations through adversarial training, so as to make the mixture of heterogeneous data more effective; representation normalization has since proven a key ingredient in multilingual transfer learning.
The same basic techniques (parameter sharing, automatic domain identification / normalization) are simultaneously at play in \cite{Zeng18multidomain,Su19exploring}: in this approach, the lower layers of the MT use auxiliary classification tasks to disentangle domain specific representations on the one hand from domain-agnostic representations on the other hand. These representations are then processed as two separate inputs, then recombined to compute the translation.
